Simulation

### 2022-11-16 Quarto_Simulation/index.qmd
Add Quarto version

```{r See session info}
#| code-fold: true
r_platform_table <- sessioninfo::platform_info()

>>>>

```{r See session info}
#| code-fold: true

# Taken from https://github.com/r-lib/sessioninfo/issues/75
get_quarto_version <- function() {
  if (isNamespaceLoaded("quarto")) {
    path <- quarto::quarto_path()
    ver <- system("quarto -V", intern = TRUE)
    if (is.null(path)) {
      "NA (via quarto)"
    } else {
      paste0(ver, " @ ", path, "/ (via quarto)")
    }
  } else {
    path <- Sys.which("quarto")
    if (path == "") {
      "NA"
    } else {
      ver <- system("quarto -V", intern = TRUE)
      paste0(ver, " @ ", path)
    }
  }
}

r_platform_table <- sessioninfo::platform_info()
r_platform_table[["quarto"]] <- get_quarto_version()[1]
